The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-05-29 ms.tex
Finish paragraph on triple systems

>>>>

A large fraction of planetary nebulae show deviations from axisymmetry \citep{Soker:2001a}.
In the cases where these deviations are moderate,
then they may be explained by binary interactions in which the stars are on eccentric orbits,
or the presence of hot or cold spots in the AGB star envelope \citep{Soker:2002b}.
Other cases, where the nebular asymmetries occur only at the outer boundary,
are probably due to interaction with the interstellar medium \citep{Ali:2012a}.
However, a significant minority (\(\sim 10\%\)) of nebulae show such large deviations from bipolar symmetry \citep{Bear:2017a}
that it has been proposed that interacting triple systems are responsible for their shaping \citep{Soker:2004b, Glanz:2020a}.
NGC~6210 falls into this category and has been proposed to be the outcome of either a ``tight binary in a wide orbit'' or a ``tight binary merger'' scenario \citep{Soker:2016b}.
However, given the multitude of evolutionary pathways available in hierarchical triple systems \citep{Toonen:2016a, Toonen:2020a},
other scenarios are also possible.

ADD is of order 3 for N, O, and Ne \citep{Bohigas:2015c}
